---
title: "Cagatay-Kiyici-503-Detailed Analysis"
author: "Cagatay Kiyici"
date: "09 01 2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANG = "en")
library(tidyverse)
library(lubridate)
library(stringi)
library(readxl)
library(ggrepel)
#library(qwraps2)
#library(writexl)
# library(matsindf)
# library(TTR)
library(zoo)
library(tsibble)
# library(xts)
# library(quantmod)
# library(tidyquant)
# library(data.table)
# library(timeDate)
# library(bizdays)
#library(swfscMisc)


```


#Detailed charts and analysis for Is Yatirim Data


```{r}
df=readRDS("df_clean.rds")

```


Recommended companies by sector
```{r}
df$Sector=fct_infreq(df$Sector)
df %>% 
  ggplot() +
 aes(x = Sector) +
 geom_bar() +
  geom_text(aes(label = ..count..), stat = "count", vjust = 1.5, colour = "white")+
 scale_fill_hue() +
 # labs(y = "# Companies", title = "title", subtitle = "subtitle", caption = "caption", fill = "fill label") +
 theme_minimal() +
 theme(legend.position = "bottom")

```

Recommended companies by recommendation type
```{r}

df %>% 
  ggplot() +
 aes(x = Recommendation, fill=Recommendation) +
 geom_bar() +
  geom_text(aes(label = ..count..), stat = "count", vjust = 1.5)+
 scale_fill_hue() +
 labs(y = "# Companies", title = "title", subtitle = "subtitle", caption = "caption", fill = "fill label") +
 theme_minimal() +
 scale_fill_manual(values=c( "green", "blue", "red"))+
 theme(legend.position = "bottom")

```


Recommended companies by industry and recommendation type
```{r}
df$Sector=fct_infreq(df$Sector)
df$Recommendation=fct_infreq(df$Recommendation)


df %>% 
  ggplot() +
 geom_bar() +
  aes(x = Sector, fill = Recommendation)+
 scale_fill_hue() +
 geom_text(aes(x = Sector, fill=Recommendation, label = ..count..),stat = "count", position=position_stack(vjust =0.9),check_overlap = TRUE)+
 labs(y = "# Companies", title = "title", subtitle = "subtitle", caption = "caption", fill = "fill label") +
 theme_minimal() +
scale_fill_manual(values=c("green", "blue", "red"))+

 theme(legend.position = "bottom")

```



market cap distribution histogram 
```{r}

ggplot(df) +
 aes(x = Market_Cap) +
 geom_histogram(bins = 10L, fill = "#0c4c8a") +
 labs(x = "asda", y = "asda", title = "asd", subtitle = "asd", caption = "ads") +
 theme_minimal() 
 


```


market cap distribution histogram by sectors
```{r}

ggplot(df) +
 aes(x = Market_Cap) +
 geom_histogram(bins = 5L, fill = "#0c4c8a") +
 labs(x = "asda", y = "asda", title = "asd", subtitle = "asd", caption = "ads") +
 theme_minimal() +
 facet_grid(vars(Sector), vars())


```


market cap distribution histogram by recommendation
```{r}

ggplot(df) +
 aes(x = Market_Cap) +
 geom_histogram(bins = 5L, fill = "#0c4c8a") +
 labs(x = "asda", y = "asda", title = "asd", subtitle = "asd", caption = "ads") +
 theme_minimal() +
 facet_grid(vars(Recommendation), vars())


```



market cap distribution histogram by sector and recommendation
```{r}

ggplot(df) +
 aes(x = Market_Cap) +
 geom_histogram(bins = 5L, fill = "#0c4c8a") +
 labs(x = "asda", y = "asda", title = "asd", subtitle = "asd", caption = "ads") +
 theme_minimal() +
 facet_grid(vars(Sector), vars(Recommendation))


```

Market cap distribution by industry recommendation

```{r}
ggplot(df) +
 aes(x = Sector, y = Market_Cap) +
 geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 0.75  ,fill=NA , aes(colour=Recommendation)) +
geom_boxplot(outlier.shape = NA)+
 # labs(x = "sfsfs", y = "sdfsdfsd", title = "sfsdf", subtitle = "sfdsdfs", caption = "sfsfsdf") +  
  scale_colour_manual(values=c("green", "blue", "red"))+
    theme_minimal()+
  theme(legend.position = "bottom")



```

Recommendation dates: pretty similar date. Only 1 recommendation was added on December. All others were update on 26th of November 2020.
```{r}
df %>% group_by(Rec_Date) %>% summarise(count=n()) %>% arrange(desc(count))

```





Let's calculate change in quarterly target price change % and net profit estimation change % for a better comparison
```{r}
df=df %>% mutate(Target_Price_Change_Lastquarter_percent=round(Target_Price_Change_Lastquarter/(Target_Price-Target_Price_Change_Lastquarter)*100,0),Netprofit_Estimate_Change_Lastquarter_percent=round(Netprofit_Change_Lastquarter/abs((Current_Estimate_Netprofit-Netprofit_Change_Lastquarter))*100,0))

```

Upside potential vs target price change % (by market cap)

```{r}



ggplot(df) +
 aes(x = Target_Price_Change_Lastquarter_percent , y = Upside, colour = Recommendation, size = Market_Cap) +
 geom_point() +
 scale_color_hue() +
 # labs(x = "asdasd", y = "asdasd", title = "adssad", subtitle = "asdasd", caption = "asdasd", color = "asdasd", size = "asdsada") +
 theme_minimal() +
  scale_colour_manual(values=c("green", "blue", "red"))+
 theme(legend.position = "bottom")

```


```{r}



ggplot(df) +
 aes(x = Target_Price_Change_Lastquarter_percent , y = Upside, colour = Sector) +
 geom_point() +
  geom_text_repel(aes(label = Stock), size = 2)+
 scale_color_hue() +
 # labs(x = "asdasd", y = "asdasd", title = "adssad", subtitle = "asdasd", caption = "asdasd", color = "asdasd", size = "asdsada") +
 theme_minimal() +
 theme(legend.position = "bottom")

```


```{r}



ggplot(df) +
 aes(x = Market_Cap , y = Upside, colour = Recommendation) +
 geom_point() +
  # geom_text_repel(aes(label = Stock), size = 2)+
 scale_color_hue() +
 # labs(x = "asdasd", y = "asdasd", title = "adssad", subtitle = "asdasd", caption = "asdasd", color = "asdasd", size = "asdsada") +
  scale_colour_manual(values=c("green", "blue", "red"))+
 theme_minimal() +
 theme(legend.position = "bottom")

```



```{r}

ggplot(df) +
 aes(y = Target_Price_Change_Lastquarter_percent , x = Netprofit_Estimate_Change_Lastquarter_percent , colour = Recommendation) +
 geom_point() +
  geom_text_repel(aes(label = Stock), size = 2)+
 scale_color_hue() +
 # labs(x = "asdasd", y = "asdasd", title = "adssad", subtitle = "asdasd", caption = "asdasd", color = "asdasd", size = "asdsada") +
  # scale_y_continuous(trans = 'log2')+
  scale_colour_manual(values=c("green", "blue", "red"))+
 theme_minimal() +
 theme(legend.position = "bottom")
```
